---
title: "Bibliometrico socio y humanidades sobre big data"
author: "gaston becerra"
date: "20/5/2020"
output: 
  html_document:
    toc: true
    toc_depth: 3
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  comment = '', fig.width = 6, fig.height = 6
  )

options(scipen = 999)

library(tidyverse)
library(igraph)
library(ggraph)
library(tidygraph)

metadata <- readr::read_csv(file = "../data/metadata.csv")
ocr <- readr::read_csv(file = "../data/ocr.csv")
autores <- readr::read_csv(file = "../data/autores.csv")

```


# Corpus

voy dejando un draft de los codigos para los analisis, con mi dataset de articulos sobre big data en sociales y humanidades

## Construccion

### ebsco

AB "big data" -----> 998?

Limitadores: Publicaciones académicas (arbitradas)

http://web.a.ebscohost.com/ehost/results?vid=35&sid=c6bcf694-e759-4265-adf8-a43b7f6949b0%40sessionmgr4008&bquery=AB+%22big+data%22&bdata=JkF1dGhUeXBlPWlwLHNoaWImZGI9ZWZ0JmRiPWhtciZkYj1laXImZGI9YWZ0JmRiPWhmdCZkYj1oc3ImZGI9c3NmJmRiPXNpaCZkYj1wYmgmbGFuZz1lcyZ0eXBlPTAmc2VhcmNoTW9kZT1TdGFuZGFyZCZzaXRlPWVob3N0LWxpdmU%3d

Education Full Text (H.W. Wilson)	637
Social Sciences Full Text (H.W. Wilson)	521
SocINDEX with Full Text	481
Psychology and Behavioral Sciences Collection	234
Art Full Text (H.W. Wilson)	81
Humanities Full Text (H.W. Wilson)	76

http://search.ebscohost.com/login.aspx?direct=true&bquery=AB+big+data&cli0=DISCIPLINE&clv0=LO+system.dis-comm%7eLO+system.dis-econ%7eLO+system.dis-ethn%7eLO+system.dis-geog%7eLO+system.dis-hist%7eLO+system.dis-lang%7eLO+system.dis-mark%7eLO+system.dis-posc%7eLO+system.dis-pogv%7eLO+system.dis-psyc%7eLO+system.dis-reli%7eLO+system.dis-sshu%7eLO+system.dis-sowo%7eLO+system.dis-socy%7eLO+system.dis-wofe&cli1=LA99&clv1=eng&athens.asp&lang=es&type=1&searchMode=And&site=eds-live&scope=site

http://search.ebscohost.com/login.aspx?direct=true&bquery=AB+big+data&cli0=DISCIPLINE&clv0=LO+system.dis-comm%7eLO+system.dis-econ%7eLO+system.dis-ethn%7eLO+system.dis-geog%7eLO+system.dis-hist%7eLO+system.dis-lang%7eLO+system.dis-mark%7eLO+system.dis-posc%7eLO+system.dis-pogv%7eLO+system.dis-psyc%7eLO+system.dis-reli%7eLO+system.dis-sshu%7eLO+system.dis-sowo%7eLO+system.dis-socy%7eLO+system.dis-wofe&cli1=LA99&clv1=eng&authtype=athens&lang=es&type=1&searchMode=And&site=eds-live&scope=site

eligiendo disciplinas

AB "BIG DATA"

language == english

### scopus

hay 5657 document results en scopus
(los bajo x año)

ABS("big data") AND SUBJAREA(ARTS OR BUSI OR DECI OR ECON OR PSYC OR SOCI) AND ( LIMIT-TO ( DOCTYPE,"ar" ) ) AND ( LIMIT-TO ( PUBYEAR,2020) ) AND ( LIMIT-TO ( LANGUAGE,"English" ) ) 

TITLE-ABS-KEY ( "big data" )  AND  DOCTYPE ( ar  OR  re )  AND  ( LIMIT-TO ( SUBJAREA ,  "SOCI" )  OR  LIMIT-TO ( SUBJAREA ,  "ARTS" )  OR  LIMIT-TO ( SUBJAREA ,  "PSYC" ) )  AND  ( LIMIT-TO ( LANGUAGE ,  "English" ) ) 

https://www.scopus.com/results/results.uri?sort=plf-f&src=s&sid=ac4c3315e766a601efe562f876cf93b0&sot=a&sdt=a&cluster=scosubjabbr%2c%22SOCI%22%2ct%2c%22ARTS%22%2ct%2c%22PSYC%22%2ct%2bscolang%2c%22English%22%2ct&sl=47&s=TITLE-ABS-KEY%28%22big+data%22%29+AND+DOCTYPE%28ar+OR+re%29&origin=searchadvanced&editSaveSearch=&txGid=2323dfe5e6d8a53e08aaa922448913f7

(entre con acceso de untref)

### jstor

hay 2135

"big data" (no abs: solo 10%) -----> hay que refinar esta busqueda?

content --- journals
Search Term(s): (ab:("big data")) AND la:(eng OR en)
Subject(s): Agriculture (2), American Studies (1), Anthropology (3), Archaeology (1), Art & Art History (1), Asian Studies (3), Business (13), Communication Studies (3), Cultural Studies (1), Economics (10), Education (5), Finance (1), General Science (22), Geography (8), History (4), History of Science & Technology (4), International Relations (12), Language & Literature (2), Law (11), Library Science (2), Management & Organizational Behavior (4), Marketing & Advertising (3), Military Studies (5), Museum Studies (1), Music (2), Peace & Conflict Studies (15), Philosophy (5), Political Science (22), Psychology (1), Science & Technology Studies (3), Sociology (24), Statistics (10), Transportation Studies (1), Urban Studies (3)

## Muestra / metadatos

```{r muestra, echo=FALSE, message=FALSE, warning=FALSE}

source("9_sample_stats.R", local = knitr::knit_global())

```

# Preguntas

## Productivity

### Time evolution of Productivity

The total number of articles found was XXXX
As it can be noted in Graph 1, the greatest production took place in the xxxxx

```{r tiempo, echo=FALSE, message=FALSE, warning=FALSE}

table(metadata %>% filter(tag=="year") %>% pull(value)) %>% plot()

```

### Increase rate

As shown in Figure 2, over the past six years, the number of publications on big data increased steadily, with an average rate of 89.7 percent. Especially from 2013, the incremental number of publications has almost doubled compared with the previous year, while after 2014 the increasing rate slows down. In 2018, the number of the articles published accounted for 31.3 percent of the sample, which was the highest point

no encontró su pico
post CA?


## Colaboración entre autores

### Authorship trend

What is the average number of authors per pub- lications?
distribution of citation (zipf law?)

```{r, echo=FALSE, message=FALSE, warning=FALSE}

# cantidad de autores
autores %>% group_by(id) %>% 
  summarize(n=n()) %>% 
  group_by(n) %>% summarise(f=n()) %>% plot()

# mas de 10 autores
autores %>% group_by(id) %>% 
  summarize(n=n()) %>% filter(n>10) %>% arrange(desc(n)) %>% pull(id)

# promedio de autores por año
autores %>% left_join(
  metadata %>% filter(tag=="year") %>%
    select(id,year=value)) %>% 
  group_by(year,id) %>% summarise(n=n()) %>%
  group_by(year) %>% summarise(avg=mean(n))

# cuantos autores por año
autores %>% left_join(
  metadata %>% 
    filter(tag=="year") %>%
    select(id,year=value)) %>% 
  group_by(year,id) %>% summarise(autores=n()) %>%
  group_by(year,autores) %>% summarise(f=n()) %>%
  ggplot(aes(y=f,x=autores)) + geom_col() + facet_wrap(~year,scales = "free_y")

```

For the complete time frame (2008 − 2017), the average number of authors per
publication is 3.45 with a standard deviation of 2.34. 13.67% of articles are
published with a single authorship, and 41% of articles have more than the
average number of authors, i.e., 41% of publications have at least 4 authors.
The surprising aspect of the findings is the share of publications with more
than 10 authors. We found that 1% of the papers have more than 10 authors.
Fig. 4 summarizes the number of authors per publication distribution.

We also analyzed the evolution of number of authors per research publications over the selected time frame. We observe that during the initial years
(2008 − 2012) 27% of publications have single authorship. During the later
years, the single authorship trend declines. In 2016 only 11.6% of papers have
single authorship, the minimum for the selected time frame. Fig. 5 depicts the
authorship trends for the time frame. It should be noted that as the number of publications are significantly lower for initial years, the data for years
2008 − 2012 is combined for reporting purposes

---> aca sube la produccion y la cantidad de autores por articulo 
(ultimos años 1 no es el mas alto )

(se puede poner la media como linea vertical en cada año?)

### Índice de Subramanyam (IS) 

Corresponde a la proporción de artículos con autoría múltiple (2 o más autores).

Se calcula a partir de la siguiente ecuación:

IS = Nm / Nm + Ns

donde:
Nm = Número de artículos con autoría múltiple
Ns = Número de artículos con autoría simple (1 autor)
El valor máximo que puede alcanzar este índice es 1 y corresponde a que todos
los artículos publicados por la revista tienen al menos dos autores

```{r, echo=FALSE, message=FALSE, warning=FALSE}
# cuantos autores por año
subra <- autores %>% left_join(
  metadata %>% 
    filter(tag=="year") %>%
    select(id,year=value)) %>% 
  group_by(year,id) %>% summarise(autores=n()) %>%
  group_by(year,autores) %>% summarise(f=n()) %>%
  pivot_wider(names_from = year, values_from=f) %>% arrange(autores) 

print("Número de Artículos Distribuidos Según Número de Autores y por Período")
subra %>% janitor::adorn_totals(where = c("row","col")) 

# colSums(subra[,1:10], na.rm = TRUE) 
Ns <- colSums(subra[which(subra$autores==1),2:14], na.rm = TRUE)
Nm <- colSums(subra[which(subra$autores>1),2:14], na.rm = TRUE)
Nm / (Nm+Ns)

# estoy hay que integrarlo a la tabla anterior y agrupar los numeros de autores

```

### Índice de Lawani (IL)

Corresponde a la media ponderada de autores por artículo, distribuidos por los
períodos de publicación definidos. Se calcula a partir de la siguiente ecuación:

$ IL = \sum_{i=1}^{N} j_i . n_j / N $

esta formula me quedó rarisima

donde:
N = Número total de artículos
ji = Número de autores por artículo
nj = Número de artículos con autoría múltiple (2 o más autores)
No existe un valor máximo para este índice

```{r eval=FALSE, message=FALSE, warning=FALSE, include=FALSE}

articulos <- autores %>% distinct(id) %>% pull(id)
N = length(articulos)
years <- autores %>% left_join(
  metadata %>% 
    filter(tag=="year") %>%
    select(id,year=value)) %>%
  distinct(year) %>% pull()
years 

for (y in 1:length(years)){
  for (i in 1:3) {
    print("----------")
    print(years[y])
    print("----------")
    
    autores2 <- autores %>% left_join(
      metadata %>% 
        filter(tag=="year") %>%
        select(id,year=value)) %>%
        filter(year==years[y])
    
    (
      #ji = Número de autores por artículo
      ji = autores2 %>% filter(id==articulos[i]) %>% pull(autor) %>% length
    )
    print(ji)
    (
      # nj = Número de artículos con autoría múltiple (2 o más autores)
      nj = autores2 %>% count(id) %>% filter(n>1) %>% pull(id) %>% length
    )
    print(nj)
    print (
      ji * nj / nrow(autores2)
    )
    print("----------")
  }
}



# cuantos autores por año
subra <- autores %>% left_join(
  metadata %>% 
    filter(tag=="year") %>%
    select(id,year=value)) %>% 
  group_by(year,id) %>% summarise(autores=n()) %>%
  group_by(year,autores) %>% summarise(f=n()) %>%
  pivot_wider(names_from = year, values_from=f) %>% arrange(autores) 
subra %>% janitor::adorn_totals(where = c("row","col")) 

# colSums(subra[,1:10], na.rm = TRUE) 
Ns <- colSums(subra[which(subra$autores==1),2:14], na.rm = TRUE)
Nm <- colSums(subra[which(subra$autores>1),2:14], na.rm = TRUE)
Nm / (Nm+Ns)

```

**2do: calcular. igual hay algo raro. no aclara ponderado por qué... será que hay que "normalizarlo" a diferencia de art/años?**

Consistente con la idea de una tendencia hacia la colaboración, el índice de Subramanyam (IS), que calcula la proporción de artículos con dos o más autores sobre el total de documentos, muestra el progresivo incremento en la proporción de artículos en colaboración, desde un 54% en el período 1992-1996 hasta un 82% en el período 2012-2016. Por otra parte, el índice de Lawani (IL) permite complementar la noción acerca de la colaboración, calculando la media ponderada de autores por artículo en cada período. En este sentido, los resultados indican que junto con un incremento en la cantidad de artículos en coautoría, el incremento en la colaboración se ha traducido en un mayor número de autores por artículo, pasando de 1,9 autores en el período 1992-1996 a 3,4 en el período 2012-2016 (ver Tabla 3). Tomados en conjunto, ambos índices sugieren que no solo ha aumentado la proporción de artículos en los que aparecen dos o más autores firmantes, sino que también ha aumentado el número de autores firmantes por artículo.

### Colaboración entre paises

antes que nada: Which countries and institutions have contributedmost in terms ofpublications count?

```{r echo=FALSE, message=FALSE, warning=FALSE}

autores %>% 
  filter(!is.na(pais)) %>%
  count(pais, sort = TRUE) %>% 
  head(30) %>%
  ggplot(aes(y=n,x=reorder(pais,n))) + geom_col() +
  coord_flip() +
  labs(title="ranking +30 paises")

# autores %>% 
#   left_join(
#   metadata %>% 
#     filter(tag=="year") %>%
#     select(id,year=value)) %>%
#   filter(!is.na(pais)) %>%
#   count(pais, year, sort = TRUE) %>% 
#   pivot_wider(names_from = year, values_from=n) %>%
#   head(10)

autores %>% 
  left_join(
  metadata %>% 
    filter(tag=="year") %>%
    select(id,year=value)) %>%
  filter(!is.na(pais)) %>% 
  count(pais, year, sort = TRUE) %>% 
    filter(n>1) %>%
    ggplot(aes(x=year,y=pais,fill=n)) + geom_tile()

```

```{r echo=FALSE, message=FALSE, warning=FALSE}

paises_corr <- autores %>% 
  filter(!is.na(pais)) %>%
  group_by(pais) %>% filter(n() > 50) %>% ungroup() %>%  
  widyr::pairwise_count(item = pais, feature = id, sort = TRUE) 

paises_corr_graph <- tidygraph::as_tbl_graph(
  paises_corr,
  directed = FALSE) %>%
  activate(nodes) %>% 
  inner_join( autores %>% group_by(pais) %>% summarise(f=n())
              , by=c("name"="pais") ) 

paises_corr_graph

paises_corr_graph %>% create_layout( layout = "kk") %>%
  ggraph::ggraph(layout) + 
  geom_edge_link(aes(width = n), alpha = 0.2, color="gray") + 
  geom_node_point(aes(size = f)) +
  geom_node_text(aes(label = name), size = 4, repel = TRUE) +
  theme_graph() +
  labs(title = "coautoria entre paises (x frecuencia)",
       subtitle = "paises con mas de 50 articulos") 

paises_corr <- autores %>% 
  filter(!is.na(pais)) %>%
  group_by(pais) %>% filter(n() > 50) %>% ungroup() %>%  
  widyr::pairwise_cor(item = pais, feature = id, sort = TRUE, method = "pearson")

paises_corr_graph <- tidygraph::as_tbl_graph(
  paises_corr %>% filter(
    correlation>0
    ), # correlaciones arriba de .1
  directed = FALSE) %>%
  activate(nodes) %>% 
  inner_join( autores %>% count(pais), by=c("name"="pais") )

paises_corr_graph %>% create_layout( layout = "kk") %>%
  ggraph::ggraph(layout) + 
  geom_edge_link(aes(width = correlation), alpha = 0.2, color="gray") + 
  geom_node_point(aes(size = n)) +
  geom_node_text(aes(label = name), size = 4, repel = TRUE) +
  theme_graph() +
  labs(title = "coautoria entre paises (x pearson)") 


```


```{r colaboracion-mapa}


# library(ggmap)
# Sys.setenv(google_key = "AIzaSyAGSGP7CUWpxDJkxjVe_UKGaV0U1Ea0gn0")
# register_google(key = Sys.getenv("google_key"))
# pp <- V(paises_corr_graph) %>% as.character()
# geoloc <- ggmap::geocode(location = pp)
# geoloc$pais <- pp
# geoloc %>% write.csv("../data/geoloc.csv")

# https://datascience.blog.wzb.eu/2018/05/31/three-ways-of-visualizing-a-graph-on-a-map/
# https://rstudio-pubs-static.s3.amazonaws.com/339257_fd4db2366a1f4e44ae95a0fd6db24457.html
# http://dyerlab.github.io/popgraph/

paises <- autores %>% 
  filter(!is.na(pais)) %>%
  count(pais, sort = TRUE)

glimpse(paises)

library(rgeos)
library(rworldmap)

wmap <- getMap(resolution="high")
centroids <- gCentroid(wmap, byid=TRUE)
paises2 <- as.data.frame(centroids)
map_world <- map_data(map = "world") %>%
  filter(region != "Antarctica")

maptheme <- theme(panel.grid = element_blank()) +
  theme(axis.text = element_blank()) +
  theme(axis.ticks = element_blank()) +
  theme(axis.title = element_blank()) +
  theme(legend.position = "bottom") +
  theme(panel.grid = element_blank()) +
  theme(panel.background = element_rect(fill = "#596673")) +
  theme(plot.margin = unit(c(0, 0, 0, 0), 'cm'))

country_shapes <- geom_polygon(aes(x = long, y = lat, group = group),
                               data = map_data('world'),
                               fill = "#c9c9c9", color = "#515151",
                               size = 0.15)
mapcoords <- coord_fixed(xlim = c(-150, 180), ylim = c(-55, 80))





paises_corr <- autores %>% 
  filter(!is.na(pais)) %>%
  group_by(pais) %>% filter(n() > 50) %>% ungroup() %>%  
  widyr::pairwise_count(item = pais, feature = id, sort = TRUE) 

paises_corr_graph <- tidygraph::as_tbl_graph(
  paises_corr,
  directed = FALSE) %>%
  activate(nodes) %>% 
  inner_join( autores %>% group_by(pais) %>% summarise(f=n())
              , by=c("name"="pais") ) 

# paises_corr_graph %>% create_layout( layout = "kk") %>%
#   ggraph::ggraph(layout) + 
#   geom_edge_link(aes(width = n), alpha = 0.2, color="gray") + 
#   geom_node_point(aes(size = f)) +
#   geom_node_text(aes(label = name), size = 4, repel = TRUE) +
#   theme_graph() +
#   labs(title = "coautoria entre paises (x frecuencia)",
#        subtitle = "paises con mas de 50 articulos") 


# en estos dos estoy perdiendo el weight, f o lo que sea

nodes <- paises_corr_graph %>% 
  activate(nodes) %>%
  inner_join(
    rownames_to_column(paises2, "name") %>% mutate(name=tolower(name))
    ) %>% 
  mutate(id=row_number()) %>%
  select(id,name,lon=x,lat=y) %>%
  as_tibble() 

edges <- paises_corr_graph %>% 
  activate(edges) %>% 
  #rename(weights=n) %>%
  distinct() %>%
  as_tibble() %>% 
  filter(from < 30, to < 30) #hay paises sin docs?

g <- graph_from_data_frame(d = edges, 
                           directed = FALSE, 
                           vertices = nodes)

edges_for_plot <- edges %>%
  inner_join(nodes %>% select(id, lon, lat), by = c('from' = 'id')) %>%
  rename(x = lon, y = lat) %>%
  inner_join(nodes %>% select(id, lon, lat), by = c('to' = 'id')) %>%
  rename(xend = lon, yend = lat)

nodes$weight = degree(g)

node_pos <- nodes %>%
  select(lon, lat) %>%
  rename(x = lon, y = lat)   # node positions must be called x, y

ggplot(nodes) + country_shapes +
  geom_curve(aes(x = x, y = y, xend = xend, yend = yend,
                 size=correlation),
             data = edges_for_plot, 
             curvature = 0.33, alpha = 0.5) +
  #scale_size_continuous(guide = FALSE) + # scale for edge widths
  #scale_size_continuous(guide = FALSE, range = c(0.25, 2)) + # scale for edge widths
  geom_point(aes(x = lon, y = lat, fill=weight),           # draw nodes
             shape = 21, 
             fill = 'white',
             color = 'black', stroke = 0.5) +
  #scale_size_continuous(guide = FALSE) +    # scale for node size
  #scale_size_continuous(guide = FALSE, range = c(1, 6)) +    # scale for node size
  geom_text(aes(x = lon, y = lat, label = name, color=weight),             # draw text labels
            hjust = 0, nudge_x = 1, nudge_y = 4,
            #size = 3,
            #color = "white", 
            fontface = "bold") +
  mapcoords + maptheme

# va queriendo. tengo que poner el peso de los links, 
# y rever porque no está usa (debo estar usando correlaciones o algo asi)

```


### ranking afiliaciones

```{r echo=FALSE, message=FALSE, warning=FALSE}

academicAff <- "universi|college|school|institu|academ|politec"

cleanAff <- function(txt) {
  z <- c()
  for(i in 1:length(txt)){
    if (!is.na(txt)){
      txt2 <- str_split(string = txt[i], pattern = ",", simplify = TRUE) %>%
        as.character()
      txt3 <- grepl(
          pattern = academicAff, 
          txt2, ignore.case = TRUE)
      if(TRUE %in% txt3) {
        z <- c(z, trimws(txt2[max(which(txt3==TRUE))]))  
      } else {
        z <- c(z, trimws(txt2[1]))
      }
    } else {
      z <- c(z, NA)
    }
  } 
  return(z)  
}

autores2 <- autores %>% 
  filter(!is.na(aff)) %>%
  mutate(
    uni = grepl(
      pattern = academicAff, 
      aff, ignore.case = TRUE),
    aff2 = cleanAff(aff)
    ) 

autores2 %>% count(uni,sort=TRUE) 

autores2 %>% 
  count(uni,aff2) %>% group_by(uni) %>% 
  mutate(aff2=str_sub(aff2,1,15))%>%
  slice_max(n = 20, order_by=n) %>%
  ggplot(aes(y=n,x=reorder(aff2,n),fill=uni)) + geom_col() +
  coord_flip() +
  facet_wrap(~uni,scales = "free")+
  labs(title="ranking universidades y empresas")

autores2 %>% 
  filter(!is.na(aff)) %>%
  count(aff2, uni, sort = TRUE) %>% 
  mutate(aff2=str_sub(aff2,1,15))%>%
  ggplot(aes(y=n,x=reorder(aff2,n),fill=uni)) + geom_col() +
  facet_wrap(~uni,scales = "free")+
  labs(title="ranking +30 aff que son o no universidades")+
  coord_flip()

# en todos estos calculos hay que ver si estamos hablando de instituciones
# o de investigadores en instituciones

```

### Colaboración académica-corporativa

Co-authorship by ACC. Among the collaborative papers, 112 (2.8 percent) are
produced through the manner of ACC. Due to the small amount of publications on this topic, this finding is likely to indicate that, in the field of big data research, joint work contributed by both academia and industry is not popular. 
Table I outlines the top 10 institutions and countries/regions in the form of ACC publication. As listed in Table I, six of the institutions are affiliated with the USA, whereas the other four are relevant to China and Switzerland. In terms of countries, the USA ranks at the top with over half ACC publications (60/54 percent). China (24/21 percent), the UK (14/13 percent) and Canada (12/11 percent) have published more than ten ACC articles. The countries do not have a big representation in ACC articles.


```{r echo=FALSE, message=FALSE, warning=FALSE}

acc <- autores2 %>% count(id,uni) %>% 
  pivot_wider(names_from = uni, values_from = n) %>%
  rename(academy=2,private=3) %>%
  mutate( acc=case_when(
    !is.na(academy) & !is.na(private) ~ "acc",
    !is.na(academy) & is.na(private) ~ "pure_academy",
    is.na(academy) & !is.na(private) ~ "pure_private"
    )
  )

acc %>% count(acc)  # cuantos puros y cuantos acc

autores2 %>% inner_join(
    acc %>% select(id,acc)
  ) %>%
  filter(acc=="acc") %>%
  count(uni,aff2) %>% group_by(uni) %>% 
  slice_max(n = 20, order_by=n) %>%
  mutate(aff2=str_sub(aff2,1,15))%>%
  ggplot(aes(y=n,x=reorder(aff2,n),fill=uni)) + geom_col() +
  coord_flip() +
  facet_wrap(~uni,scales = "free_y")+
  labs(title="top instituciones que hacen ACC")

```




